\section {Awards}
\label{sec:Awards}

\subsection{Main Competition Awards}
Prizes will be awarded to the teams that are placed highest at the end of the competition.
The teams in $1^{st}$, $2^{nd}$ and $3^{rd}$ place will receive awards.

\subsection{Rookie Award}
The Rookie Award will be awarded to the rookie
team\footnote{A rookie team is one from a school, college or independent group that hasn't competed in Student Robotics before.}\addtocounter{footnote}{-1}\addtocounter{Hfootnote}{-1}
 that places highest in the league.

\subsection{Committee Award}
The Committee Award will be given to the team that displays the most extraordinary ingenuity in the design of their robot.
It will not be awarded for complexity of design, rather the implementation of a simple and elegant solution to a problem.

\subsection{Robot and Team Image}
The team that presents their robot and themselves in what is judged to be the most outstanding way will receive this award.

\subsection{First Robot Movement}
The first rookie team\footnotemark{} that demonstrates a moving robot to the community will be awarded with an edible prize at the final competition.
\begin{enumerate}
\item The robot movement must be controlled by software running on the Student Robotics kit.
\item The robot must move 2 metres, pause for 2 seconds, turn 180$^\circ$ ($\pm20^\circ$), return to its starting position ($\pm0.5m$), and come to a halt without interference.
\item This must be demonstrated by a video on the web (e.g. on YouTube, flickr, etc.) and linking to this video from a post on the Student Robotics forum.
\end{enumerate}

\subsection{Online Presence}
The team that is judged to have the best online presence will be awarded with an edible prize at the final competition.
 An online presence is a publicly available set of web pages detailing the team's progress, it can involve blog posts, pictures and videos of the team and the robot.
 \emph{Hint: Useful sites include blogger.com, wordpress.com, flickr.com and youtube.com}
\begin{enumerate}
\item When detailing activities online do not post any private information concerning yourself or others.
\item Notify Student Robotics about the location of your online materials on the Student Robotics forums.
\end{enumerate}
