\documentclass[a4paper, 11pt]{scrartcl}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage{booktabs}

% hyperref and nameref so that we can have sane internal refs
% hyperref also helps with pdf index creation
\usepackage[linkcolor={blue},citecolor={blue},urlcolor={red}]{hyperref}
\usepackage{nameref}

% Place all of the figures at the end of the document
\usepackage[figuresonly,nomarkers,nolists]{endfloat}
\renewcommand{\efloatseparator}{}

% Set to false for black/white printing
\hypersetup{colorlinks=true}

\title {Student Robotics 2013\\ Rulebook}
\author{Revision 6}
\date{\today}
\setcounter{tocdepth}{1}

\begin {document}
\maketitle

\noindent The following defines the rules and regulations of the Student Robotics 2013 competition.

\newcounter{rule}[section]
\newcommand{\rcn}{\stepcounter{rule}\arabic{section}.\arabic{rule}}
\renewcommand{\labelenumi}{\rcn}

\input {game-rules}
\newpage
\input {regs}
\newpage
\input {specs}
\newpage
\input {awards}

\renewcommand{\labelenumi}{\rcn}

\section{Clarifications}
Requests for rule clarifications may be sent to \href{mailto:info@studentrobotics.org}{\nolinkurl{info@studentrobotics.org}}.
Requests received within one month of the competition are unlikely to be processed.

%% The following changes have been made to the rules since their initial release:

\begin{enumerate}
\item 2012-11-12: Added the Rookie Award \& made the First Robot Movement Award only available to Rookie teams.
\item 2013-01-08: Clarified the height of a pedestal with regards to the rim around the top.
\item 2013-02-05: Clarified that only the robot must fit within a $500mm$ cube before the start of a match. A token placed in/on the robot is not included.
\item 2013-03-14: Delay the date by which teams must request to keep their kits until the 30th of March 2013.
\item 2013-04-02: Add appendix detailing safety regulations.
\end{enumerate}

\newpage
\appendix
\appendixpage
\addappheadtotoc
\input {kit-return}
\input {safety-regs}

\end {document}
